On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-01 manuscripts/PNAS/chazthm_pnas.tex
almost a complete draft

A similar phenomenon applies to sets of vectors with a stable sparse representation. As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.

@@

\begin{definition}\label{dDef}
For any point $\mathbf{u}$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$ be the distance of $\mathbf{u}$ from the set $V$. For subspaces $U,V \subseteq \mathbb{R}^m$, we define: %[Kato p.197]
\begin{align}\label{d}
d(U,V) := \sup_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 = 1} \text{\rm dist}(\mathbf{u},V).
\end{align}
Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case, set $d(\{\textbf{0}\},V) = 0$ for any $V$.
\end{definition}
%Note that the supremum is always achievable by a point in $U$ when $U, V \subseteq \mathbb{R}^m$.

@@

Our result in combinatorial matrix analysis is the following.

@@

\begin{lemma}\label{MainLemma}
Fix integers $n$ and $k < m$, and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition}. There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq {[m] \choose k}$ satisfying the SIP there exists a map $\pi: E \mapsto {[m] \choose k}$ satisfying:
\begin{align}\label{GapUpperBound}
d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon,\ \ \   \text{for all $S \in E$},
\end{align}
%
then there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ with:
\begin{align}\label{MainLemmaBPD}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for all } j \in [m].
\end{align}
\end{lemma}

The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by:
\begin{align}\label{Cdef1}
C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
\end{align}
%
where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S) := \{i : \text{supp}(\mathbf{x}_i) = S\}$.\footnote{We can be sure $C_1 > 0$ is well-defined (provided $C_2$ is well-defined) since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$ and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.} The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of a technical quantity related to one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
% for projecting a point onto the intersection of a set of subspaces. 
We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.

@@

The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
\begin{align}\label{Cdef2}
C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{i \in [m]} \|\mathbf{A}_i\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
\end{align}
%Note that when $k=1$ the constant $C_1$ is consistent with the value in our proof of the case $k=1$.

\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$. Fix $S \in E$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.

%%% No |S| = k assumption %%%
We begin by showing that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$. Fix $S \in E$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in I(S)$ are contained in $S$ and $S'$, respectively.

Let $\mathbf{X}$ and $\mathbf{\hat{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively. It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{J(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{J(S)}$ are linearly independent and thus form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$. Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there then exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{J(S)}\mathbf{c}$. Letting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{J(S)}\mathbf{c}$}, which is in $\text{\rm Span}\{\mathbf{B}_{S'}\}$, we have:
\begin{align*}
\|\mathbf{y} - \mathbf{\hat{y}}\|_2 
&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{I(S)} - \mathbf{B\hat{X}}_{I(S)})_i\|_2
\leq \varepsilon \sum_{i=1}^k |c_i| \\
&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
%\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
\leq \frac{\varepsilon}{L_k(\mathbf{AX}_{I(S)})} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality is by definition of $L_k$. It follows that for all $S \in E$,
\begin{align}\label{rhs222}
d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\}) 
\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
%\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
%&< \left( \frac{ L_2(\mathbf{A}) }{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2 } \right) \frac{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } { L(\mathbf{AX}_{J(S)}) } \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) \\
\end{align}
The result then follows by  Lem.~\ref{MainLemma}, with the map $\pi: E \to {[m] \choose k}$ defined by the association $S \mapsto S'$ above.
%\begin{align}
%\delta= \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } = \frac{ C \varepsilon }{ \tilde C } < \frac{L_2(\mathbf{A})}{\tilde C}
%\end{align}
\end{proof}

@@

% FRITZ: Inverse problems instead of Data Analysis. Don't assume that everyone is assuming they are recovering ground truth. Cite results again and state implications! Focus on them (probabilistic ones too).
\textbf{Inverse Problems}.  
Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel} (e.g., recovering a rat's position on a linear track from local field potentials in Hippocampus \cite{Agarwal14}). It would be of practical utility therefore to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes. %We encourage researchers to extend our results and tighten these parameters.
Phrased in the language of Hadamard \cite{Hadamard1902}),  Mention sparse matrix factorization. [Effective computation of stable datasets, at least in principle.]
[maybe smooth analysis something here]

@@

\textbf{Engineering}.
Several groups utilize compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}. Given such effective uses of compressed sensing, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data. Guarantees such as those offered by our theorems allow any such device to be equivalent to any other (having different initial parameters and data samples) as long as enough data originate from a statistically identical system.

As a final remark, we hope that researchers in sparse linear coding continue to improve on the bounds and constants here.

@@

\begin{lemma}\label{SpanIntersectionLemma}
Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq 2^{[m]}$ of rank $k$:
\begin{align*}
\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \cap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
\end{align*}
\end{lemma}
\begin{proof}
By induction, it is enough to prove the lemma when $|F| = 2$. The proof now follows directly from the assumption.
\end{proof}

% This can be made tighter by using Pythagoras' Thm for first projection instead of triangle inequality. 
\begin{lemma}\label{DistanceToIntersectionLemma}
Fix $k \geq 2$. Let $V_1, \ldots, V_k$ be subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$. For every $\mathbf{x} \in \mathbb{R}^m$, we have:
\begin{align}\label{DTILeq}
\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{r(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i),
\end{align}
where $r$ is given in Def.~\ref{SpecialSupportSet}.
\end{lemma}
\begin{proof} 
Fix $\mathbf{x} \in \mathbb{R}^m$ and $k \geq 2$. Recall that the orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V$ from $\mathbb{R}^m$ to $V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
% Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection

We begin the proof by observing that:
%Use Pythagoras' Theorem first?
\begin{align}\label{f}
\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 &\leq \|\mathbf{x} - \Pi_{V_k} \mathbf{x}\|_2 + \|\Pi_{V_k}  \mathbf{x} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{x}\|_2 \nonumber \\
&\ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{x} - \Pi_V \mathbf{x}\|_2 \nonumber \\
&\leq \|\Pi_{V_k}\cdots\Pi_{V_{1}} \mathbf{x} - \Pi_V \mathbf{x}\|_2 + \sum_{\ell=1}^k \|\mathbf{x} - \Pi_{V_{\ell}} \mathbf{x}\|_2,
\end{align}
%
by the triangle inequality and the fact that the spectral norm $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$ (since $\Pi_{V_{\ell}}$ are orthogonal projections).

@@

Substituting this into \eqref{f} and rearranging yields \eqref{DTILeq} after substituting $r(\{V_i\}_{i=1}^k)$ for $1 - z$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
\end{proof}

\begin{lemma}\label{NonEmptyLemma} 
Fix integers $\ell$ and $m \leq \hat m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property. If there exists a map $\pi: E \to 2^{[\hat m]}$ such that $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
\begin{align}\label{cond}
|\cap_{S \in F} \pi(S)| \leq |\cap_{S \in F} S |,\ \ \   \text{for all } F \subseteq E,
\end{align}
%
then the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $[J]$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$. In particular, if $\hat m = m$ then the map $\pi$ is induced by a permutation.
%$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
\end{lemma}
\begin{proof}
[* TODO * Chris rewrite for $\hat m$] Fix $T = \{(j, S): j \in \pi(S), S \in E\}$. We have $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$. Note that by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular. Pigeonholing the elements of $T$ with respect to the set of possible first indices, we see then that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.

@@

\begin{proof}[Proof of Main Lemma]
We first claim $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ for all $S \in E$. To see why, note that the right-hand side of \eqref{GapUpperBound} is then strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq 1$ by \eqref{delrho}. By \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$). It follows that the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent and, by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
\begin{align}\label{eq2}
d(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_S\} ) = d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}).
\end{align}
We will now show that:
\begin{align}\label{fact2}
|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } \ F \subseteq E.
\end{align}

>>>>

A similar phenomenon applies to sets of vectors with a stable sparse representation. As in \cite[Sec.~IV]{Hillar15}, consider the ``symbolic'' dataset $Y = \{\mathbf{A}\mathbf{x}_1,\ldots,\mathbf{A} \mathbf{x}_N\}$ generated by indeterminate $\mathbf{A}$ and indeterminate $k$-sparse $\mathbf{x}_1, \ldots, \mathbf{x}_N$.

@@

\begin{definition}\label{dDef}
For $\mathbf{u} \in \mathbb R^m$, let $\text{\rm dist}(\mathbf{u}, V) := \inf \{\| \mathbf{u}-\mathbf{v} \|_2: \mathbf{v} \in V\}$, and for subspaces $U,V \subseteq \mathbb{R}^m$, define\footnote{Although identical, note the reference \cite{Morris10} defines the supremum over the unit ball.}: %[Kato p.197]
\begin{align}\label{d}
d(U,V) := \sup_{\mathbf{u} \in U, \ \|\mathbf{u}\|_2 = 1} \text{\rm dist}(\mathbf{u},V).
\end{align}
Note that $d(U,\{\textbf{0}\}) = 1$ for $U \neq \{\mathbf{0}\}$, whereas if $U = \{\textbf{0}\}$ then $d$ has no meaning; in this case, set $d(\{\textbf{0}\},V) = 0$ for any $V$.
\end{definition}
%Note that the supremum is always achievable by a point in $U$ when $U, V \subseteq \mathbb{R}^m$.

@@

Our result in combinatorial matrix theory is the following.

@@

\begin{lemma}\label{MainLemma}
Fix integers $n$ and $k < m$, and suppose $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfies the spark condition \eqref{SparkCondition}. There exists a constant $C_2 > 0$ for which the following holds for all $\varepsilon < L_2(\mathbf{A}) / C_2$. If for some  $\mathbf{B} \in \mathbb{R}^{n \times m}$ and regular $E \subseteq {[m] \choose k}$ with the SIP there exists a map $\pi: E \mapsto {[m] \choose k}$ satisfying:
\begin{align}\label{GapUpperBound}
d(\text{\rm Span}\{\mathbf{A}_{S}\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \leq \varepsilon,\ \ \   \text{for all $S \in E$},
\end{align}
%
then there exists a permutation matrix $\mathbf{P}$ and invertible diagonal matrix $\mathbf{D}$ with:
\begin{align}\label{MainLemmaBPD}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 \leq C_2 \varepsilon, \ \ \  \text{for all } j \in [m].
\end{align}
\end{lemma}

The constant $C_1$ in Thm.~\ref{DeterministicUniquenessTheorem} is then given by\footnote{We can be sure $C_1 > 0$ since $L_k(\mathbf{A}), L_k(\mathbf{X}_{I(S)}) > 0$ by the spark condition and general linear position of the $\mathbf{x}_i$; hence $\|\mathbf{A}_j\|_2 > 0$ for all $j$ and for all $S \in E$ we have $\|\mathbf{AX}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A})\|\mathbf{X}_{I(S)}\mathbf{c}\|_2 \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)})\|\mathbf{c}\|_2$ for all $k$-sparse $\mathbf{c}$, and therefore $L_k(\mathbf{AX}_{I(S)}) \geq L_k(\mathbf{A}) L_k(\mathbf{X}_{I(S)}) > 0$.}:
\begin{align}\label{Cdef1}
C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E) := \frac{ C_2(\mathbf{A}, E) } { \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) },
\end{align}
%
where $\mathbf{X}$ is the $m \times N$ matrix with columns $\mathbf{x}_i$ and $I(S)$ is defined as those $i \in [N]$ with supports in $S$. The constant $C_2 = C_2(\mathbf{A}, E)$ is defined below in terms of one used in \cite{Deutsch12} to analyze the convergence of the alternating projections algorithm.
% for projecting a point onto the intersection of a set of subspaces. 
We use it to bound the distance between a point and the intersection of a set of subspaces given an upper bound on its distance from each subspace individually.

@@

The constant $C_2$ in Lem.~\ref{MainLemma} can then be expressed as:  % \footnote{Note that $C_2 > 0$ is well-defined since $r > 0$ by definition.}
\begin{align}\label{Cdef2}
C_2(\mathbf{A}, E) := \frac{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2}{ \min_{F \subseteq E} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) }.
\end{align}
%Note that when $k=1$ the constant $C_1$ is consistent with the value in our proof of the case $k=1$.

\begin{proof}[Proof of Thm.~\ref{DeterministicUniquenessCorollary} for $k < m$] 
%We begin by showing that for every $S \in E$ there is some $S' \in {[m] \choose k}$ for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_S'\})$ is controlled by $\varepsilon$. Fix $S \in E$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $J(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in J(S)$ are contained in $S$ and $S'$, respectively.
%%% No |S| = k assumption %%%
We shall show that for every $S \in E$ there is some $S' \subseteq [m]$, $|S'| \leq k$, for which the distance $d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\})$ is controlled by $\varepsilon$. Since there are $(k-1){m \choose k}+1$ vectors $\mathbf{x}_i$ supported on $S$, the pigeon-hole principle implies that there exists some $S' \in {[m] \choose k}$ and some set of $k$ indices $I(S)$ such that the supports of all $\mathbf{x}_i$ and $\mathbf{\hat x}_i$ with $i \in I(S)$ are contained in $S$ and $S'$, respectively.

Let $\mathbf{X}$ and $\mathbf{\hat{X}}$ be the $m \times N$ matrices with columns $\mathbf{x}_i$ and $\mathbf{\hat x}_i$, respectively. It follows from the general linear position of the $\mathbf{x}_i$ and the linear independence of every $k$ columns of $\mathbf{A}$ that $L_k(\mathbf{AX}_{I(S)}) > 0$; that is, the columns of the $n \times k$ matrix $\mathbf{AX}_{I(S)}$ form a basis for $\text{\rm Span}\{\mathbf{A}_{S}\}$. Fixing $\mathbf{y} \in \text{\rm Span}\{\mathbf{A}_{S}\}$, there exists a unique $\mathbf{c} = (c_1, \ldots, c_k) \in \mathbb{R}^k$ such that $\mathbf{y} = \mathbf{AX}_{I(S)}\mathbf{c}$. Setting \mbox{$\mathbf{\hat{y}} = \mathbf{B\hat{X}}_{I(S)}\mathbf{c} \in \text{\rm Span}\{\mathbf{B}_{S'}\}$}, we have:
\begin{align*}
\|\mathbf{y} - \mathbf{\hat{y}}\|_2 
&= \|\sum_{i=1}^k c_i(\mathbf{AX}_{I(S)} - \mathbf{B\hat{X}}_{I(S)})_i\|_2
\leq \varepsilon \sum_{i=1}^k |c_i| \\
&\leq \varepsilon \sqrt{k}  \|\mathbf{c}\|_2 
%\leq \frac{\varepsilon \sqrt{k}}{L(\mathbf{A}X_{J(S)})} \|\mathbf{A}X_{J(S)}\mathbf{c}\|_2 
\leq \frac{\varepsilon}{L_k(\mathbf{AX}_{I(S)})} \|\mathbf{y}\|_2,
\end{align*}
where the last inequality is by definition of $L_k$. Also, from Def.~\ref{dDef}, it follows that for all $S \in E$,
\begin{align}\label{rhs222}
d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{S'}\}) 
\leq \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) }.
%\leq \frac{\varepsilon}{L(\mathbf{AX}_{J(S)})}.
%&< \left( \frac{ L_2(\mathbf{A}) }{ 2^{|E|} \max_{j \in [m]} \|\mathbf{A}_j\|_2 } \right) \frac{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } { L(\mathbf{AX}_{J(S)}) } \min_{\substack{F \subseteq E}} r( \{ \text{\rm Span}\{\mathbf{A}_{S}\} \}_{S \in F}) \\
\end{align}
Finally, applying Lem.~\ref{MainLemma} with the map $\pi: E \to {[m] \choose k}$ defined by $S \mapsto S'$ above completes the proof.
%\begin{align}
%\delta= \frac{\varepsilon}{ \min_{S \in E} L_k(\mathbf{AX}_{I(S)}) } = \frac{ C \varepsilon }{ \tilde C } < \frac{L_2(\mathbf{A})}{\tilde C}
%\end{align}
\end{proof}

@@

% FRITZ: Inverse problems instead of Data Analysis. Don't assume that everyone is assuming they are recovering ground truth. Cite results again and state implications! Focus on them (probabilistic ones too).
\textbf{Inverse Problems}.  
Our results provide theoretical grounding for the use of sparse linear coding in blind source separation, wherein the goal is to infer the generating dictionary and sparse codes from noisy measurements generated as in \eqref{LinearModel} (e.g., recovering a rat's position on a linear track from local field potentials in Hippocampus \cite{Agarwal14}). It would be of practical utility therefore to determine the best possible dependence of $\varepsilon$ on $\delta_1, \delta_2$ (see \eqref{epsdel}) as well as the minimal requirements on the number and diversity of generating codes. %We encourage researchers to extend our results and tighten these parameters.
Phrased in the language of Hadamard \cite{Hadamard1902}),  Mention sparse matrix factorization. [Effective computation of stable datasets, at least in principle.]
[maybe smooth analysis something here]
We hope that researchers in sparse linear coding continue to improve on the bounds and constants here.

@@

\textbf{Engineering}.
Several groups utilize compressed sensing for signal processing tasks: MRI analysis \cite{lustig2008compressed},  image compression \cite{Duarte08}, and, more recently, the design of an ultrafast camera \cite{Gao14}. Given such effective uses of CS, it is only a matter of time before these systems incorporate sparse dictionary learning to encode and process data. Guarantees such as those offered by our theorems allow any such device to be equivalent to any other (having different initial parameters and data samples) as long as enough data originate from a statistically identical system.

@@

\begin{lemma}\label{SpanIntersectionLemma}
Let $\mathbf{M} \in \mathbb{R}^{n \times m}$. If every $2k$ columns of $\mathbf{M}$ are linearly independent, then for any $F \subseteq {[m] \choose k}$:
\begin{align*}
\text{\rm Span}\{\mathbf{M}_{\cap F}\}  = \cap_{S \in F} \text{\rm Span}\{\mathbf{M}_S\}.
\end{align*}
\end{lemma}
\begin{proof}
By induction, it is enough to prove the lemma when $|F| = 2$. The proof now follows directly from the assumption.
\end{proof}

% This can be made tighter by using Pythagoras' Thm for first projection instead of triangle inequality. 
\begin{lemma}\label{DistanceToIntersectionLemma}
Fix $k \geq 2$. Let $V_1, \ldots, V_k$ be subspaces of $\mathbb{R}^m$ and set $V = \cap_{i = 1}^k V_i$. For every $\mathbf{x} \in \mathbb{R}^m$, we have:
\begin{align}\label{DTILeq}
\text{\rm dist}(\mathbf{x}, V) \leq \frac{1}{r(\{V_i\}_{i = 1}^k)} \sum_{i=1}^k \text{\rm dist}(\mathbf{x}, V_i),
\end{align}
where $r$ is given in Def.~\ref{SpecialSupportSet}.
\end{lemma}
\begin{proof} 
Recall that orthogonal projection onto a subspace $V \subseteq \mathbb{R}^m$ is the mapping $\Pi_V: \mathbb{R}^m \to V$ that associates with each $\mathbf{x}$ its unique nearest point in $V$; i.e., $\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 = \text{\rm dist}(\mathbf{x}, V)$.
% Since subspaces of real vector spaces are closed, we can replace inf with min in def. of orthogonal projection

We begin the proof by observing:
%Use Pythagoras' Theorem first?
\begin{align}\label{f}
\|\mathbf{x} - \Pi_V\mathbf{x}\|_2 &\leq \|\mathbf{x} - \Pi_{V_k} \mathbf{x}\|_2 + \|\Pi_{V_k}  \mathbf{x} - \Pi_{V_k}\Pi_{V_{k-1}}\mathbf{x}\|_2 \nonumber \\
&\ \ \ + \cdots + \|\Pi_{V_k} \Pi_{V_{k-1}}\cdots \Pi_{V_1} \mathbf{x} - \Pi_V \mathbf{x}\|_2 \nonumber \\
&\leq \|\Pi_{V_k}\cdots\Pi_{V_{1}} \mathbf{x} - \Pi_V \mathbf{x}\|_2 + \sum_{\ell=1}^k \|\mathbf{x} - \Pi_{V_{\ell}} \mathbf{x}\|_2,
\end{align}
%
using the triangle inequality and that the spectral norm satisfies $\|\Pi_{V_{\ell}}\|_2 \leq 1$ for all $\ell$ (since $\Pi_{V_{\ell}}$ are orthogonal projections).

@@

Substituting this into \eqref{f} and rearranging yields \eqref{DTILeq} after replacing $1 - z$ with $r(\{V_i\}_{i=1}^k)$ (as $z$ may depend on the arbitrary ordering of the $V_i$).
\end{proof}

\begin{lemma}\label{NonEmptyLemma} 
Fix $\ell$ and $m \leq \hat m$. Suppose $E \subseteq 2^{[m]}$ is $\ell$-regular and satisfies the singleton intersection property. If there is a map $\pi: E \to 2^{[\hat m]}$ with $\sum_{S \in E} |S| = \sum_{S \in E} |\pi(S)|$ and:
\begin{align}\label{cond}
|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } F \subseteq E,
\end{align}
%
then the association $i \mapsto \cap \pi(F(i))$ defines an injective map from $[J]$ to $[\hat m]$ for some $J \subseteq [m]$ of size $\hat m - \ell(\hat m - m)$. In particular, if $\hat m = m$ then the map $\pi$ is induced by a permutation.
%$\pi(E)$ is $\ell$-regular and satisfies the singleton intersection property. In particular, $|\cap_{S \in F} S| = 1$ if and only if $|\cap_{S \in F} \pi(S)| = 1$. 
\end{lemma}
\begin{proof}
[* TODO * Chris rewrite for $\hat m$] Fix $T = \{(j, S): j \in \pi(S), S \in E\}$. We have $|T| = \sum_{S \in E} |\pi(S)| = \sum_{S \in E} |S| = \sum_{i \in [m]} \deg(i) = \ell m$ by regularity of $E$. Note that by \eqref{cond} there can be no more than $\ell$ elements of $T$ with a given first index, since $E$ is $\ell$-regular. Pigeonholing the elements of $T$ with respect to the set of possible first indices, we see then that for each $j$ there must be exactly $\ell$ elements of $T$ with $j$ as a first index; hence, $\pi(E)$ is $\ell$-regular.

@@

\begin{proof}[Proof of Main Lemma]
We first claim $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ for all $S \in E$. To see why, note that the right-hand side of \eqref{GapUpperBound} is then strictly less than one, since $r \leq 1$ and $L_2(\mathbf{A}) \leq 1$ by \eqref{delrho}. By \eqref{dimLem}, it then follows that $|\pi(S)| \geq \dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) \geq \dim(\text{\rm Span}\{\mathbf{A}_{S}\}) = |S|$, with the equality due to $\mathbf{A}$ satisfying \eqref{SparkCondition}; hence, $\dim(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}) = \dim(\text{\rm Span}\{\mathbf{A}_{S}\})$ (since $|S| = |\pi(S)|$). It follows that the columns of $\mathbf{B}_{\pi(S)}$ are linearly independent and, by \eqref{eqdim}:% and $\mathbf{B}_i \neq \textbf{0}$ for all $i$.
\begin{align}\label{eq2}
d(\text{\rm Span}\{\mathbf{B}_{\pi(S)}\}, \text{\rm Span}\{\mathbf{A}_S\} ) = d(\text{\rm Span}\{\mathbf{A}_S\}, \text{\rm Span}\{\mathbf{B}_{\pi(S)}\}).
\end{align}
We will now show that \eqref{cond} holds.
%\begin{align}\label{fact2}
%|\bigcap_{S \in F} \pi(S)| \leq |\bigcap_{S \in F} S |,\ \ \   \text{for all } \ F \subseteq E.
%\end{align}
